\section{Introduction}

\begin{frame}[plain]
  \titlepage
  \vspace{-0.5em}
  \hfill{\tiny Manrique et al., \textit{Science Advances} 2:e1501742 (2016)}

  \note{
    \textbf{Time: 0:30}\par
    This talk is based almost entirely on one paper.\par
    Signal the topic is sensitive and that the presentation treats extremist networks academically, not operationally.\par
    Preview: two case studies and two notions of centrality.
  }
\end{frame}

\begin{frame}{Motivation: who is central in extreme networks?}
  \small
  \begin{columns}[T,onlytextwidth]
    \begin{column}{0.55\textwidth}
      \begin{block}{Research question}
        \begin{itemize}
          \item Common stereotype: women are peripheral in dangerous settings.
          \item The paper asks whether \alert{network position} tells a different story.
          \item Two cases: online pro-ISIS support and offline PIRA operations.
        \end{itemize}
      \end{block}

      \begin{exampleblock}{Analytical focus}
        Contrast local hub-like visibility with \alert{betweenness-based brokerage}.
      \end{exampleblock}
    \end{column}

    \begin{column}{0.42\textwidth}
      \begin{block}{Key claim}
        Even in male-dominated networks, women can occupy connectivity positions that support robustness and survival.
      \end{block}

      \vspace{0.35em}

      \centering
      \begin{tikzpicture}
        \node[draw=PresTwoMuted,rounded corners,fill=PresTwoSurface,align=center,inner sep=8pt,text width=0.78\linewidth]
        {Guiding question\\[0.25em]\textbf{Who holds the network together}\\under pressure?};
      \end{tikzpicture}
    \end{column}
  \end{columns}

  \note{
    \textbf{Time: 2:00}\par
    Contrast local visibility with collective importance.\par
    Say explicitly this is about network roles, not notoriety.\par
    Preview degree versus betweenness as the core comparison.
  }
\end{frame}

\begin{frame}{Ethical scope and interpretive guardrails}
  \begin{alertblock}{Scope}
    The analysis concerns \textbf{network-science measurement} rather than operational guidance.
  \end{alertblock}

  \begin{block}{Interpretive guardrails}
    \begin{itemize}
      \item Keep visuals at the level of abstracted network structure; do not reproduce extremist media.
      \item Use descriptive, non-sensational language.
      \item Separate empirical findings from causal or normative overreach.
    \end{itemize}
  \end{block}

  \note{
    \textbf{Time: 1:00}\par
    Set the boundary conditions before the technical material starts.\par
    Then move directly to the centrality definitions.
  }
\end{frame}
